### 2021-02-25 architecture.tex
Fix caption of CNF graph schema
Improve diagram of example graph

\begin{figure}[h]
\caption{CNF network schema}
\label{fig:CnfSchema}
\centering
\tikzstyle{token} = [rectangle, draw]

@@

\begin{figure}[h]
\caption{Graph representation of the \gls{cnf} formula $a=b \wedge f(a,b) \neq f(b,b)$.}
\label{fig:GcnExample}
\centering
\digraph[scale=0.3]{GcnExample}{
	node [fontsize=32, shape=record];
	edge [fontsize=32, dir=both, arrowtail=empty];
	problem [label=<problem|a=b &and; f(a,b)&ne;f(b,b)>];
	c0 [label="clause|a=b"];
	c1 [label=<clause|f(a,b)&ne;f(b,b)>];
	problem -> c0;
	problem -> c1;
	t0 [label="equality atom|a=b"];
	t1 [label="equality atom|f(a,b)=f(b,b)"];
	c0 -> t0 [label=" + "];
	c1 -> t1 [label=" &ndash; "];
	ta [label="term|a"];
	tb [label="term|b"];
	ff [label="function|f", style=bold];
	fa [label="function|a", style=bold];
	fb [label="function|b", style=bold];
	tfab [label="term|f(a,b)"];
	tfbb [label="term|f(b,b)"];
	tfab0 [label="argument|1", style=dotted];
	tfab1 [label="argument|2", style=dotted];
	tfbb0 [label="argument|1", style=dotted];
	tfbb1 [label="argument|2", style=dotted];
	t0 -> ta;
	t0 -> tb;
	t1 -> tfab;
	t1 -> tfbb;
	tfab -> ff;
	tfab -> tfab0;
	tfab0 -> tfab1;
	tfab0 -> ta;
	tfab1 -> tb;
	tfbb -> ff;
	tfbb -> tfbb0;
	tfbb0 -> tfbb1;
	tfbb0 -> tb;
	tfbb1 -> tb;
	ta -> fa;
	tb -> fb;
}
\end{figure}

>>>>

\begin{figure}[h]
\caption{\gls{cnf} graph schema}
\label{fig:CnfSchema}
\centering
\tikzstyle{token} = [rectangle, draw]

@@

\begin{figure}[h]
\caption{Graph representation of the \gls{cnf} formula $a=b \wedge f(a,b) \neq f(b,b)$.}
\label{fig:GcnExample}
\centering
\digraph[scale=0.5]{GcnExample}{
graph [ranksep=0.3];
node [fontsize=14, shape=record, height=0, width=0];
edge [fontsize=14, dir=both, arrowtail=empty];

problem [label=<problem|a=b &and; f(a,b)&ne;f(b,b)>];

{ rank = same;
c0 [label="clause|a=b"];
c1 [label=<clause|f(a,b)&ne;f(b,b)>];
}

problem -> c0;
problem -> c1;

{ rank = same;
t0 [label="equality atom|a=b"];
t1 [label="equality atom|f(a,b)=f(b,b)"];
}

c0 -> t0 [label=" + "];
c1 -> t1 [label=" &ndash; "];

{ rank = same;
tfab [label="term|f(a,b)"];
tfbb [label="term|f(b,b)"];
}

{ rank = same;
ta [label="term|a"];
tb [label="term|b"];
}

ff [label="function|f", style=bold];
fa [label="function|a", style=bold];
fb [label="function|b", style=bold];
tfab0 [label="argument|1", style=dotted];
tfab1 [label="argument|2", style=dotted];
tfbb0 [label="argument|1", style=dotted];
tfbb1 [label="argument|2", style=dotted];
t0 -> ta;
t0 -> tb;
t1 -> tfab;
t1 -> tfbb;
tfab -> ff;
tfab -> tfab0;
tfab0 -> tfab1;
tfab0 -> ta;
tfab1 -> tb;
tfbb -> ff;
tfbb -> tfbb0;
tfbb0 -> tfbb1;
tfbb0 -> tb;
tfbb1 -> tb;
ta -> fa;
tb -> fb;

% Technical details:
%ff -> ff [dir=forward];
%fa -> fa [dir=forward];
%fb -> fb [dir=forward];
}
\end{figure}
